Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-04 paper/paper.tex
Figure 1B (IFN reporter) and supplements
Added images showing creation and validation
of the IFN reporter cell lines. These
are Figure 1B and associated supplements.

%%% start IFNrare figure %%%
\begin{figure}
\centerline{
{\bf \Large A}\includegraphics[width=0.25\textwidth,valign=t]{figures/IFN_stochastic/RussellVenn/venn_diagram.pdf}
{\bf \Large B}
}
\caption{
Triggering of IFN production is rare in influenza-infected cells.
{\bf (A)} Number of influenza-infected and IFN+ cells in our prior single-cell study of influenza infection of A549 cells.
The Venn diagram shows data aggregated over all samples from \citet{russell2018extreme}.
{\bf (B)} An A549 fluorescent-reporter cell-line confirms that IFN expression is rare in cells infected with our viral stock.
\jdbcomment{This should be a simple figure, such as a plot that just shows the fraction IFN+ among flu infected cells for a few replicates.
If you have suitable data, you could show for low, medium, and high-inducing stock and indicate which we use.
Then put detailed flow data similar to what is in your writeup in \FIGSUPP[IFNrare]{flow}. For that flow data, I think contour plots are better than overplotting. Also, don't subsample but show all points, as that will give better statistics.
We could possibly add a \emph{small simple} schematic of reporter line here as panel {\bf (B)} and move the current {\bf (B)} to {\bf (C)}, and then have more details in \FIGSUPP[IFNrare]{reporter_cells}.
Alternatively, we could just show everything in \FIGSUPP[IFNrare]{reporter_cells}.}
}
\label{fig:IFNrare}

\figsupp[Creation and validation of A549 fluorescent-reporter cell lines for type I and type III IFN expression.]
{CAPTION}
{\jdbcomment{ADD FIGURE}}
\label{figsupp:reporter_cells}

\figsupp[Expression of type I and type III IFN are highly correlated in influenza-infected A549 cells. \jdbcomment{Alternatively, we could leave this out if you don't have clean data for this point and just refer to \FIGSUPP[experiment]{type_I_III_correlation}}]
{CAPTION}
{\jdbcomment{ADD FIGURE}}
\label{figsupp:type_I_vs_III}

\figsupp[Full flow cytometry data for \FIG{IFNrare}B.]
{CAPTION}
{\jdbcomment{ADD FIGURE}}
\label{figsupp:flow}

@@

>>>>

%%% start IFNrare figure %%%
\begin{figure}
\centerline{
{\bf \Large A}\includegraphics[width=0.25\textwidth,valign=t]{figures/IFN_stochastic/RussellVenn/venn_diagram.pdf}
\hspace{0.05\textwidth}
{\bf \Large B}\includegraphics[width=0.35\textwidth,valign=t]{figures/IFN_stochastic/IFN_reporter/IFN_reporter.pdf}
\hspace{0.05\textwidth}
{\bf \Large C} \jdbcomment{ADD FIGURE PANEL}
}
\caption{
Triggering of IFN production is rare in influenza-infected cells.
{\bf (A)} Number of influenza-infected and IFN+ cells in our prior single-cell study of influenza infection of A549 cells.
The Venn diagram shows data aggregated over all samples from \citet{russell2018extreme}.
{\bf (B)} Creation of an A549 reporter cell line to efficiently identify single cells expressing IFN.
The cells are engineered to contain an IFN promoter that drives expression of a fluorescent protein and cell-surface protein amenable to MACS (magnetic-activated cell sorting).
We created reporter cell lines with both type I (IFN-$\beta$) and type III (IFN-$\lambda$) promoters (\FIGDATA[IFNrare]{reporter_sequences}).
The reporters were efficiently activated when infected with a virus known to potently induce IFN (\FIGSUPP[IFNrare]{reporter_validation}).
Expression of type I and type III IFN is highly correlated in the reporter cell lines upon infection with influenza virus (\FIGSUPP[IFNrare]{type_I_vs_III}).
{\bf (C)}
Frequency of IFN induction upon infection with the influenza virus stocks used in this paper as quantified using the reporter cell lines.
\jdbcomment{This should be a simple figure, such as a plot that just shows the fraction IFN+ among flu infected cells for the virus stocks we use, plus positive and negative controls.
Then put detailed flow data in \FIGSUPP[IFNrare]{flow}. }
}
\label{fig:IFNrare}

\figsupp[Validation of IFN reporter cell lines.]
{To validate the IFN reporter cell lines, they were infected at high MOI with the Cantell strain of Sendai virus, which strongly activates IFN expression~\citep{strahle2006sendai}.
Activation of the IFN reporter was then monitored by flow cytometry using the marker indicated at the bottom of each plot (either a fluorescent protein or antibody staining for the cell-surface LNGFR).
Sendai infection efficiently activated the IFN reporter in all cases, with the strongest signal for the IFN-$\lambda$ reporter driving ZsGreen.
}
{\includegraphics[width=0.5\textwidth]{figures/IFN_stochastic/IFN_reporter/Sendai_validation.pdf}}
\label{figsupp:reporter_validation}

\figsupp[Expression of type I and type III IFN are highly correlated in influenza-infected A549 cells.]
{A549 cells were dually transduced with the IFN-$\beta$ and IFN-$\lambda$ reporters driving expression of mCherry and ZsGreen, respectively.
The cells were then infected with two different stocks of ``wildtype'' WSN influenza, or stocks with a deletion in PB1 or stop codons in NS1 (described later in the paper).
After 13 hours, cells were analyzed by flow cytometry.
As shown in the FACS plots, expression of the IFN-$\beta$ and IFN-$\lambda$ reporters is highly correlated in all cases.}
{\includegraphics[width=0.5\textwidth]{figures/IFN_stochastic/IFN_reporter/IFNbeta_IFN_lambda_correlated.pdf}}
\label{figsupp:type_I_vs_III}

\figsupp[Full flow cytometry data for \FIG{IFNrare}C.]
{\jdbcomment{ADD CAPTION}}
{\jdbcomment{ADD FIGURE}}
\label{figsupp:flow}

@@

\figdata{Sequences of the reporters schematized in \FIG{IFNrare}B.
The MACS sortable surface marker is a truncated LNGFR.
For the IFN-$\beta$ reporter, the fluorescent protein is mNeonGreen.
For the IFN-$\lambda$ (IL29) reporter, the fluorescent protein is ZsGreen.
The sequences of plasmids carrying these reporters are at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/IFN_stochastic/IFN_reporter/1517_pHAGE2_IFNbeta_prom_LNGFR_P2A_mNeongreen.gb} and \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/IFN_stochastic/IFN_reporter/1767_pHAGE2_IL29_promnkozak_LNGFR_P2A_zsGreen.gb}.
}
\label{figdata:reporter_sequences}
